Network Configuration Synthesis with Abstract Topologies

### 2016-11-15 paper/abstraction/paper.tex
add citations

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct configurations for large, evolving networks from high-level specifications of topology, routing policy, and fault-tolerance requirements. It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the impact of topology and routing policy on fault tolerance. Our algorithms operates entirely on abstract topologies and guarantees correctness for all its concrete instantiations. \sysname also guarantees that minimal changes to existing device configurations are required when the network evolves to add or remove devices and links. Our experiments with real-world topologies and policies show that our abstractions and algorithms are effective and that, for large networks, \sysname synthesizes configurations two orders of magnitude faster than systems that operate over concrete topologies.

@@

  \vspace{1em}
  \noindent
  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
  \label{thm:concretization}
\end{thm}
%
\vspace{-.6em}
Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix. These results also help assign semantics to templates.

@@

\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}. The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations.
%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

@@

\para{Network verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.

>>>>

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct configurations for large, evolving networks from high-level specifications of topology, routing policy, and fault-tolerance requirements. It is based on new abstractions for capturing parameterized network topologies and their evolution, and algorithms to analyze the impact of topology and routing policy on fault tolerance. Our algorithms operate entirely on abstract topologies and guarantee correctness for all its concrete instantiations. \sysname also guarantees that minimal changes to existing device configurations are required when the network evolves to add or remove devices and links. Our experiments with real-world topologies and policies show that our abstractions and algorithms are effective and that, for large networks, \sysname synthesizes configurations two orders of magnitude faster than systems that operate over concrete topologies.

@@

  \vspace{1em}
  \noindent
  $\Con(\text{compile}(pol,G^A), \Gamma,f,G) = \text{compile}(\Con(pol,\Gamma,f),G)$
  \label{thm:concretization}
\end{thm}
%
\vspace{-.6em}
Full definitions of compilation and concretization, as well as the proof of Theorem~\ref{thm:concretization} are included in the appendix.

@@

\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and directly generates the forwarding rules that tell routers how to forward packets~\cite{foster:merlin,fattire,netgen}. The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

@@

\para{Network verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,ipassure,batfish,bagpipe,arc,era,surgery,coalgebraic}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.
